### 2024-03-15 sections/2homology.tex
Miniscule changes.

\begin{remark}\label{rem:disk_b=disk_bsc}
    The $\infty$-operad $\disk(\bstr)_{/M}$, so defined, does not actually depend on the $\bstr$-structure; there is an equivalence
    %
    \begin{equation}
        \disk(\bstr)_{/M} \simeq \disk(\bsc)_{/M},
    \end{equation}
    %
    where $M$ on the right-hand side is the underlying stratified manifold of the $\bstr$-manifold also called $M$. This is essentially because the $\infty$-cateogry of basics $\bstr \xrightarrow{} \bsc$ is defined as a right fibration. Intuitively, those disks that have an open embedding into $M$ admit a $\bstr$-structure by restriction since $M$ admits one. From here, since over $\infty$-groupoids are contractible, there is an equivalence between the singleton space consisting of this inherited $\bstr$-structure and the space of $\bstr$-structures the disk originally had. The argument, of course, holds for $\disk(\bstr)_{/M}$ too, as well as $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. This is why, when talking about these slice $\infty$-operads we will simplify the notation down to $\disk_{/M}$, $\disk[r]_{/M}$, $\mfld_{/M}$ and $\mfld[r]_{/M}$.
\end{remark}

@@

The next result is of key importance to the technical side of the theory, and will be used extensively throughout. It alone, is essentially the reason for the appearance of constructible bundles in a lot of later developments.

\begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a functor of $\infty$-operads
    %
    \begin{equation}
        f^{-1}: \disk_{/N} \xrightarrow{} \mfld_{/M},
    \end{equation}
    %
    which acts on objects by sending $V \xhookrightarrow{} N$ to $f^{-1}V \xhookrightarrow{} M$.
\end{lemma}

\begin{remark}
    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
\end{remark}

@@

\begin{theorem}[{\cite[thm.2.25]{aft_fhstrat}}]\label{thm:fh_pushforward}
    Let $f: M \xrightarrow{} N$ be a constructible bundle. There is a pushforward functor
    %
    \begin{equation}
        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC),
    \end{equation}
    %
    which takes a $\disk_{/M}$-algebra $A$ to
    %
    \begin{equation}
        f_*A: \disk_{/N} \xrightarrow{f^{-1}} \mfld_{/M} \xrightarrow{\int_{-} A} \catC.
    \end{equation}
    %
    This functor is such that there is a canonical equivalence in $\catC$
    %
    \begin{equation}
        \int_{M} A \simeq \int_{N} f_* A
    \end{equation}
\end{theorem}

@@

Now that we have a pushforward operation, we can finally explicitly state what excision is in this context. This is because a collar-gluing of a stratified manifold $M$ is defined exactly as a constructible bundle $f: M \xrightarrow{} [-1,1]$.

>>>>

\begin{remark}\label{rem:disk_b=disk_bsc}
    The $\infty$-operad $\disk(\bstr)_{/M}$, so defined, does not actually depend on the $\bstr$-structure; there is an equivalence
    %
    \begin{equation}
        \disk(\bstr)_{/M} \simeq \disk(\bsc)_{/M},
    \end{equation}
    %
    where $M$ on the right-hand side is the underlying stratified manifold of the $\bstr$-manifold also called $M$. This is essentially because the $\infty$-cateogry of basics $\bstr \xrightarrow{} \bsc$ is defined as a right fibration. Intuitively, those disks that have an open embedding into $M$ admit a $\bstr$-structure by restriction since $M$ admits one. From here, since over $\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), there is an equivalence between the singleton space consisting of this inherited $\bstr$-structure and the space of $\bstr$-structures the disk originally had. The argument, of course, holds for $\disk(\bstr)_{/M}$ too, as well as $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. This is why, when talking about these slice $\infty$-operads we will simplify the notation down to $\disk_{/M}$, $\disk[r]_{/M}$, $\mfld_{/M}$ and $\mfld[r]_{/M}$.
\end{remark}

@@

The next result is of key importance to the technical side of the theory, and will be used extensively throughout. It alone, is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.

\begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a functor of $\infty$-operads
    %
    \begin{equation}
        f^{-1}: \disk_{/N} \xrightarrow{} \mfld_{/M},
    \end{equation}
    %
    which acts on objects by sending $V \xhookrightarrow{} N$ to $f^{-1}V \xhookrightarrow{} M$.
\end{lemma}

\begin{remark}
    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the weakly constructible bundle $f$.
\end{remark}

@@

\begin{theorem}[{\cite[thm.2.25]{aft_fhstrat}}]\label{thm:fh_pushforward}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a pushforward functor
    %
    \begin{equation}
        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC),
    \end{equation}
    %
    which takes a $\disk_{/M}$-algebra $A$ to
    %
    \begin{equation}
        f_*A: \disk_{/N} \xrightarrow{f^{-1}} \mfld_{/M} \xrightarrow{\int_{-} A} \catC.
    \end{equation}
    %
    This functor is such that there is a canonical equivalence in $\catC$
    %
    \begin{equation}
        \int_{M} A \simeq \int_{N} f_* A
    \end{equation}
\end{theorem}

@@

Now that we have a pushforward operation, we can finally explicitly state what excision is in this context. This is because a collar-gluing of a stratified manifold $M$ is defined exactly as a weakly constructible bundle $f: M \xrightarrow{} [-1,1]$.

### 2024-03-15 sections/3algebras.tex
Miniscule changes.

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement). This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however only locally constant factorization algebras can detect the stratified structure, so in all other cases that we have considered the above functor is even an equivalence, and not just fully-faithful.
\end{remark}

>>>>

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement). This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however for the types that don't detect the stratified structure the above functor is even an equivalence, and not just fully-faithful, and is of no interest.
\end{remark}

### 2024-03-15 sections/4gluing.tex
Miniscule changes.

\begin{proof}
    The symmetric monoidal structure of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ is inherited from $\catC$ pointwise. We denote the objects of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ as $(R,A,L)$, and use $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction. Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint-preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\mathsf{Assoc^{RL}}} (\catC)^I \arrow[r, "\mathsf{B}^I"] \arrow[d, "f_*"] & \catC^I \arrow[d, "f_*"] \\
            \alg{\mathsf{Assoc^{RL}}} (\catC)^J \arrow[r, "\mathsf{B}^J"] & \catC^J.
        \end{tikzcd}
    \end{equation}

@@

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
\end{example}

>>>>

\begin{proof}
    The symmetric monoidal structure of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ is inherited from $\catC$ pointwise. We denote the objects of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ as $(R,A,L)$, and use $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction. Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint--preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\mathsf{Assoc^{RL}}} (\catC)^I \arrow[r, "\mathsf{B}^I"] \arrow[d, "f_*"] & \catC^I \arrow[d, "f_*"] \\
            \alg{\mathsf{Assoc^{RL}}} (\catC)^J \arrow[r, "\mathsf{B}^J"] & \catC^J.
        \end{tikzcd}
    \end{equation}

@@

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate triangulations of the spheres.
\end{example}
